How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-02 tse-paper/content.tex
Add motivation

>>>>

\textbf{Motivation.} The information stored in build logs can and has
already been used for a variety of applications. One prominent dataset
in the space, TravisTorrent, was featured as the MSR Data Challenge
2017~\cite{msr17challenge}. To date, scientist and practitioners alike
have used it and other, proprietary datasets to understand and
cateogrize Continuous Integration build
failures~\cite{islam2017insights}, to do research on testing
practices~\cite{orellana2017differences}, to train classifiers to
predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
and to investigate static analysis tools in CI
builds~\cite{zampetti2017open}. Therefore, being able to efficiently
and correctly extract information from build logs is paramount to the
future of a variety of fields depending on it.
